A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-10-29 README.Rmd
explain how to rebuild everything #49

>>>>

## Rebuild Everything

In case you experience some unexpected behavior with this workflow, you should check that you have the most recent version (`git pull`), rebuild the docker image (`make build`) and force the rebuild of all targets (`make -B DOCKER`).

```{bash, eval=FALSE}
git pull && make build && make -B DOCKER=TRUE
```
